Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-11-17 paper/1_Initial/manuscript.qmd
typos and headings

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    corresponding: true
    orcid: 0009-0006-0020-7599
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Magdalena Pfaff
    corresponding: true
    orcid: 0009-0006-2386-7936
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
keywords: []
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*) or urinating (e.g. *"I can always accurately perceive when I need to urinate"*).
Interestingly, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; **SECOND REF**], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).

@@

The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrasts the traditional CFA/SEM factor-based analyses with graph-based ones such as EGA.
2) The second part will provide an overview of the dispositional correlates of the IAS, sketching a pattern of associations that is key to better understand the nature, place and role of interoception questionnaires within a larger context.

@@

The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data.
Thus, providing additionally a individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.

### Method

@@

## Statistical Analysis

@@

# Results

@@

### Correlations

@@

### EGA

@@

# Discussion

@@

## Limitations and Future Directions

@@

## Methods

### Materials

@@

### Statistical analysis

@@

## Results

@@

## Discussion

@@

# References

@@

# Appendix

# Title for Appendix

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Magdalena Pfaff
    orcid: 0009-0006-2386-7936
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
keywords: []
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*) or urinating (e.g. *"I can always accurately perceive when I need to urinate"*).
Interestingly, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; **SECOND REF**], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).

@@

The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA.
2) The second part will provide an overview of the dispositional correlates of the IAS, providing an overview of the pattern of associations that is key to better understand the nature, place and role of interoception questionnaires within a larger context.

@@

The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data.
Thus, providing additionally an individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.

### Methods

@@

### Statistical Analysis

@@

### Results

@@

#### Correlations

@@

#### EGA

@@

### Discussion

@@

### Limitations and Future Directions

@@

### Methods

#### Materials

@@

#### Statistical analysis

@@

### Results

@@

### Discussion

@@

## References

@@
